### 2020-09-23 LaTeX/sections/abstract.tex
finished (collateral didn't fit)
appendix edits

\begin{abstract}
Order-driven exchanges on Ethereum tend to operate in a fully centralized fashion, or with some functionality performed on-chain (\eg loading accounts, order cancelation) and some off-chain functionality (\eg matching orders). Fully on-chain solutions have a superior threat model and were experimented with in the early days of Ethereum, but they have been largely abandoned for performance reasons. As blockchain performance continues to improve (both in research and in practice) and on-chain dealer-based exchanges like Uniswap (an alternative to order-based exchanges) rise in popularity, it seems to be an ideal time to revisit the idea of a fully on-chain order-driven exchange and benchmark what is possible performance-wise. We design and optimize an Ethereum-based call market exchange, \cm, and conduct a variety of experiments to show the current benchmark is around one hundred trade executions per block. We also explore numerous extensions for further improvements.
\end{abstract}

>>>>

\begin{abstract}
Order-driven exchanges on Ethereum tend to operate in a fully centralized fashion, or with some functionality performed on-chain (\eg loading accounts, order cancelation) and some off-chain functionality (\eg matching orders). Fully on-chain solutions have a superior threat model and were experimented with in the early days of Ethereum, but they have been largely abandoned for performance reasons. As block\-chain performance continues to improve (both in research and in practice) and on-chain dealer-based exchanges like Uniswap (an alternative to order-based exchanges) rise in popularity, it seems to be an ideal time to revisit the idea of a fully on-chain order-driven exchange and benchmark what is possible performance-wise. We design and optimize an Ethereum-based call market exchange, \cm, and conduct a variety of experiments to show the current benchmark is around one hundred trade executions per block. We also explore numerous extensions for further improvements, including a variant using off-chain execution (`rollups').
\end{abstract}

### 2020-09-23 LaTeX/sections/paper.tex
appendix edits

\subsection{Cost/Benefit of Cleaning up After Yourself}
\label{sec:gasrefund}

@@

One consequence of a linked list is that a new contract is created for every node in the list. Beyond being expensive for adding new nodes (a cost that will be bared by the trader in a call market), it also leaves a large footprint on the Ethereum blockchain, especially if we leave the nodes on the blockchain in perpetuity (\ie we just update the head node of the list and leave the previous head `dangling.'). However in a PQ, nodes are only removed from the head of the list; thus the node contracts could be `destroyed' one by one using an extra operation, \texttt{SELFDESTRUCT}, in the \texttt{Dequeue()} function. As shown in Table~\ref{tab:cleaning}, the refund from doing this outweighs to the cost of the extra computation: gas costs are reduced from 721K to 557K.  This suggests a general principle: cleaning up after yourself will pay for itself in gas refunds. Unfortunately, this is not universally true as shown by applying the same principle to the linked list with mapping.

@@

Imagine you have just launched an ERC20 token on Ethereum. Now want your holders to be able to trade it. While the barrier to entry for exchange services is low, it still exists. For a centralized or decentralized exchange, you have to convince the operators to list your token and you will be delayed while they process your request. For an automated market maker, you will have to lock up a large amount of ETH into the DApp, along with your tokens. For rollups, you will have to host your own servers or list it with an exchange. By contrast to all of these, with \cm you just deploy the code alongside your token and trading is immediately supported. Even if \cm is a fallback solution today, we believe it is helpful for every token to be accompanied by on-chain trade execution. With future improvements to blockchain scalability, it could become the defacto trading method.

>>>>

\subsection{Cost/Benefit of cleaning up after yourself}
\label{sec:gasrefund}

@@

One consequence of a linked list is that a new contract is created for every node in the list. Beyond being expensive for adding new nodes (a cost that will be bared by the trader in a call market), it also leaves a large footprint in the active Ethereum state, especially if we leave the nodes on the blockchain in perpetuity (\ie we just update the head node of the list and leave the previous head `dangling.'). However in a PQ, nodes are only removed from the head of the list; thus the node contracts could be `destroyed' one by one using an extra operation, \texttt{SELFDESTRUCT}, in the \texttt{Dequeue()} function. As shown in Table~\ref{tab:cleaning}, the refund from doing this outweighs to the cost of the extra computation: gas costs are reduced from 721K to 557K.  This suggests a general principle: cleaning up after yourself will pay for itself in gas refunds. Unfortunately, this is not universally true as shown by applying the same principle to the linked list with mapping.

@@

Imagine you have just launched an ERC20 token on Ethereum. Now want your holders to be able to trade it. While the barrier to entry for exchange services is low, it still exists. For a centralized or decentralized exchange, you have to convince the operators to list your token and you will be delayed while they process your request. For an automated market maker, you will have to lock up a large amount of ETH into the DApp, along with your tokens. For rollups, you will have to host your own servers. By contrast to all of these, with \cm you just deploy the code alongside your token and trading is immediately supported. Even if \cm is a fallback solution today, we believe it is helpful for every token to be accompanied by on-chain trade execution. With future improvements to blockchain scalability, it could become the defacto trading method.
